Work Stress

### 2023-03-16 outputs/paper/paper.qmd
Update paper to include all parts of Dicussion

@@

## A Potential Explanation: Shifting Priorities {#sec-third-point}

When it comes to the age of the population of the United States and comparing it from the past to now. It shows that more people tend to have kids much later than before. While fewer people have kids earlier than in the past. In the past, more people tend to have kids much earlier. There are several reasons why more people had kids at an early age back then; people used to get married much earlier, and many people were unemployed or doing a job for self-employment, which was not even an educated or professional job. The modern lifestyle that has been adopted in the past few decades tends to make people focus on all other areas of life, which makes them marry much later, and have kids later. Nowadays, many marriages happen at the age of late 20s or early 30s, while they tend to have their first child around the early to mid-30s. @fig-5 depicts the birth rates in women between the ages 30-39 and 35-39 positive slope trend. Whether pre or post-2007 recession, this trend looks steady over the past 40 years. This finding aligns with the current common belief and the social norm where, perhaps, women's peak childbearing ages have shifted from the early twenties to early thirties. @fig-6 shows the average number of children born to women by age in five-year intervals from the 1968-1972 through 1993-1997 birth cohorts. These birth cohorts include women entering their peak childbearing years (20--24) in 1992, 1997, 2002, 2007, and 2017. This chart indicates that the three cohorts of young adult women born between 1968 and 1982 in 1992, 1997, and 2002 had similar childbearing age profiles. The 2007 birth cohort of women had fewer children in their 20s and 30s. The 2012 and 2017 birth cohorts (born between 1988 and 1997) have significantly fewer children than the preceding cohorts. This finding is consistent with a decline in births, primarily to more recent cohorts of women. From a statistical point of view, this divergence across cohorts explains the sizable decrease in annual birth rates that began in 2007.

## Weakness and Moving Forward

### Bias and Ethical Concerns

As we know that this data was collected and created by other human beings, just as how we are. There are some ethical concerns that could affect the accuracy of our data because humans can make mistakes, and they can make decisions based on their preferences, which can affect the whole dataset. So, this analysis is only valid based on our dataset, which can be modified if the original dataset is changed.

The original data shows different races, such as White, Black, and Hispanic. They have included Hispanic based on all colours, which erases the identity of Black and Indigenous Hispanic people. This tends to be a bit of racism because the information provided on the data did not specifically indicate whether or not the Hispanic category includes everyone that identifies as Hispanic or is it just people that look Hispanic.

### Data Collection Concerns

This dataset tends to collect huge data information on the population among people from the United States and considers lots of factors from race, birth rates by age, student debts, etc. Having too much information means that when the data is collected, there is a possibility of human error, calculation error, and chances of small modification of data due format of reporting an error. So, the way how the data was collected can have lots of problems because people can make mistakes easily.

### Moving Forward

This paper raised concerns about a dramatic decline in U.S. birth rates starting in 2007. Through the paper, we proposed a general explanation for the decline in births across recent cohorts of U.S. women that focuses on the shifting priorities of cohorts. As dictated by the recent socio-phenomena that encompasses preferences for having children, life aspirations, and the nature of parenting, a change in the relationship between education and childbearing, a rise in childlessness, and the establishment of a two-child norm for those having children have irreversibly changed [@citepaper]. This new social phenomenon that might be causing the dramatic decline in U.S. birth rates is important from an economic policy standpoint to acknowledge that an aging population and shrinking workforce pose challenges to economic growth and the sustainability of social insurance systems [@Yang2003]. Thus, the most appropriate way to address declining U.S. birth rates may be required: 1. developing A.I. and robots where a shrinking workforce poses a problem, 2. an appropriate policy to address issues with Social Security and Medicare on a secure basis for the long-term. Suppose the U.S. birth rate is not showing any reverse trend shortly. In that case, the U.S. economy and political system should enforce greater emphasis on addressing the issue before it becomes irreversible.

>>>>

# Results

@@

## Conclusion

Work stress seems to be the main problem for everyone in both physical and mental health. Through our data, there was a lots of things to imaginate about the causes of work stress which is revealed throughout the paper. The causes in correlation into work stress are by factors such as job status, work hours, industry sector, and satisfaction rates. Half of the people working either full time or part time are facing work stress, and this could be because of their assigned tasks that they have to do every day. Under work hours, the higher the hours people work for, the higher amount of people facing work stress. This could be because of people working for too long, which is affecting their health condition, and that causes them to face higher levels of work stress. Government sector tends to be slightly higher than private sector for work stress, but this could be because government sectors tends to pay a bit less compared to bigger private sectors. For job satisfaction, there are some people that are often disatisfied, which reflects their work stress and this could be because they job they are working for is not suitable for them, lack of interst, commute issues, traffic delays, work schedule, etc. So, there are lots of issues in work, which is the main issue of work stress. After looking over everything, we believe that if companies within the same job industry pays the same salary, reducing the work hours to 35 hours a week, and trying to make some jobs hybrid or remote. Then, this can reduce the number of work stress people are facing every day.
